---
title: "oregon_health2"
author: "John Morse"
date: "4/16/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include = FALSE}
library(readxl)
library(janitor)
library(tidyverse)
library(gt)
library(infer)
library(psych)
library(skimr)
library(broom)
```

```{r data2, include=FALSE}
data <- read_csv("data_2/ohie_assignment2.csv") %>% 
  clean_names()
data
```

```{r question1, include = FALSE}

mean <- describe(data$ed_visits) %>% 
  select(mean)

sd <- describe(data$ed_visits) %>% 
  select(sd)

median <- describe(data$ed_visits) %>% 
  select(median)

perc_90 <- data %>% 
  pull(ed_visits) %>% 
  quantile(.90, na.rm = TRUE)

perc_99 <- data %>% 
  pull(ed_visits) %>% 
  quantile(.99, na.rm = TRUE)
```


1 *Question:* The main outcome, or dependent variable, of interest will be “ed_visits”, which is the self-reported number of Emergency Department visits during the previous 12 months. You can use the “summarize” command, along with the “detail” option, to display summary statistics for a variable. Report each of the following statistics for “ed_visits”: mean, standard deviation, median, 90th percentile, 99th percentile.


*Answer:*

Mean: **`r mean`**


Standard Deviation: **`r sd`**


Median: **`r median`**


90th Percentile: **`r perc_90`**


99th Percentile: **`r perc_99`**


```{r medicaid, include = FALSE}

mean <- describe(data$medicaid) %>% 
  select(mean)

sd <- describe(data$medicaid) %>% 
  select(sd)
```


2 *Question:* The main regressor, or independent variable, of interest will be “medicaid”, which is an indicator for whether a person was enrolled in Medicaid at the time of the survey. Note that this Medicaid enrollment indicator is not randomized. For “medicaid”, report the mean and standard deviation.

*Answer:*

Mean: **`r mean`**


Standard Deviation: **`r sd`**
